

%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
  \textbf{\Huge \scshape Kyle Mackenzie} \\ \vspace{1pt}
  \href[pdfnewwindow=true]{https://1mackenziekyle.github.io/personal-website/#}{\underline{portfolio}} $|$
  \href{mailto:1mackenziekyle@gmail.com}{\underline{1mackenziekyle@gmail.com}} $|$
  \small \href{https://github.com/1mackenziekyle}{\underline{github.com/1mackenziekyle}} $|$
  \href{https://www.linkedin.com/in/kyle-mackenzie-url/}{\underline{linkedin.com/in/kyle-mackenzie-url}} 
  % $|$ \href{https://first.github.io/}{\underline{first.github.io}}
\end{center}

 
  
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, C++, Python, HTML/CSS} \\
     \textbf{Frameworks / Packages}{: React, MongoDB, Node.js, JUnit, NumPy {\&} Pandas, Selenium} \\
     \textbf{Tools/Environments}{: Git \& Github, Jupyter Notebooks} \\
    }}
 \end{itemize}
 
    %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Engineering Phyics}{Vancouver, BC}
      {University of British Columbia}{Sep. 2020 - May 2025 (expected)}
      \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Relevant Coursework}{: Software Design, Algorithms and Data Structures, Robotics Design, Signals and Systems} \\
    }}
 \end{itemize}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Relevant Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Full-Stack Developer Co-op}{Jan. 2022 -- Apr. 2022}
      {ICBC}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Proposed, designed, and prototyped a new type of automation solution used internally that reduced development costs by 50\% compared to company standard.}
        \resumeItem{Researched and developed company standard prototype for automation solutions using Robot Framework, while cutting time to get products to customers by 50\%.}
        \resumeItem{Automated the development of test cases using Robot Framework to increase test coverage of web application, reducing development costs.}
        \resumeItem{Used ThreeJS, ExpressJS and Node to prototype a 3D, gamified version of current ICBC Knowledge Practice Test to increase customer engagement and learning, and improve road safety.}
      \resumeItemListEnd
  \resumeSubheading
      {Drivetrain Firmware Developer}{Sep. 2022 -- Present}
      {UBC Formula Electric Student Design Team}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Developing traction control algorithms in C for STM microcontrollers, for real-time autonomous stabilization in slipping accidents.}
        \resumeItem{Researched and documented experimental control algorithms for high-performance electric cars.}
      \resumeItemListEnd


    \resumeSubheading
      {Front-End Developer}{May 2021 -- Sep. 2021}
      {Charlene's Web Services}{Remote}
      \resumeItemListStart
        \resumeItem{Developed a slideshow application using JS, express.js, HTML/CSS for deployment on WordPress marketplace.}

      \resumeItemListEnd
      
      
    \resumeSubheading
      {Embedded Systems Developer}{Jan. 2021 -- Sep. 2021}
      {UBC Solar Student Design Team}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Helped develop multi-threaded communication firmware in C for micro-controllers to communicate through serial, radio, and cellular for real-time data acquisition during solar car races.}
        \resumeItem{Wrote documentation for embedded software algorithm to ensure complete understanding for future employees.}
        
      \resumeItemListEnd

      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Technical Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Social Network Analysis Project}
          $|$ \emph{3 person project - Java, Git, JUnit}
          }{Oct. 2021}
          \resumeItemListStart
            \resumeItem{Developed a Graph data structure to represent relationships between co-workers from a company's email records.}
            \resumeItem{Implemented methods for depth-first and breadth-first search, as well as finding the shortest path between 2 users.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{Autonomous Robot}
          $|$ \emph{C, Arduino, STM32}
          }{Aug. 2021}
          \resumeItemListStart
            \resumeItem{Designed and built embedded software system for an autonomous robot that interacted directly with sensors and actuators}
            \resumeItem{Designed and soldered a Butterworth bandpass filter circuit to clean an Infrared signal before software processing}
            \resumeItem{Developed tape-following PID Motor Control Algorithm for custom-fabricated robot}
            \resumeItem{Designed, soldered, and tested PCBs for all of the robot's electrical systems}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Image Classifier} 
          $|$ \emph{Python, TensorFlow, Google Colab Notebooks} 
          }{Sep. 2020 -- Oct. 2020}
          \resumeItemListStart
            \resumeItem{Developed a Convolutional Neural Network with TensorFlow to classify images of clothing items}
            \resumeItem{Achieved a 90\%+ Accuracy}
          \resumeItemListEnd
          
        %  \resumeItemListEnd
         
    \resumeSubHeadingListEnd

%-------------INTERESTS--------------------
\section{Interests}

    \small{Hiking \textbullet \ Robotics \textbullet \  Music Production \textbullet \ Web Design }

%-------------------------------------------
\end{document}
